\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{multirow, tabularx}
\usepackage{enumitem}
\usepackage[
    top = 1.0cm,
    bottom = 1.0cm,
    left = 1.0cm,
    right = 1.0cm
]{geometry}

\pagestyle{empty}
\renewcommand{\familydefault}{\sfdefault}

\setlist[itemize]{leftmargin=0pt}
\setlist[enumerate]{leftmargin=0pt}
\setlist[description]{leftmargin=0pt}

\usepackage[usenames, dvipsnames]{xcolor}

\begin{document}
\noindent
{\LARGE \textsf{\fontfamily{ptm}\selectfont \textbf{Gylmar Moreno}}}
\hfill \begingroup\hypersetup{hidelinks}
\href{mailto:contact@gylmar.com}{\small contact@gylmar.com}\endgroup\\
\hspace*{0pt} \hfill \begingroup\hypersetup{hidelinks}
\href{tel:+13479210474}{\small (347) 921-0474}\endgroup
\vspace{-.5cm}

\begin{description}
    \item[\textsf{\fontfamily{ptm}\selectfont SUMMARY}]
        \hfill
        \vspace{-.3cm}
        \noindent\rule{\linewidth}{1.0pt}
        Software engineer with proven track record of bridging complex backend
        systems to constrained low-latency consumer interfaces (biometrics,
        handhelds, smart carts). Cross-functional collaborator with
        Engineering, Product, Data, Security, and Quality teams that delivers
        backward from customer stories for MVPs, system extensions, and system
        scaling alike. Implements data-driven systems with end-to-end metrics
        and monitoring across mission-critical services and tracking KPIs to
        ensure operational excellence.

    \item[\textsf{\fontfamily{ptm}\selectfont WORK EXPERIENCE}]
        \hfill
        \vspace{-.3cm}
        \rule{\linewidth}{1.0pt}
        \vspace{-.8cm}
        \begin{description}

        \item[Amazon - AWS]
        \hfill
        \textit{May 2022 - June 2024}
        \vspace{-.1cm}
        \begin{itemize}[leftmargin=*]
            \item Led and mentored team to deliver an external service endpoint
                  for Amazon One (\textit{AO}) Enterprise devices to perform
                  secure badge-in through a seamless palm hover authentication
                  for a customer pool managed on the AWS Console. It securely
                  managed sensitive customer Palm Images, Biometric IDs, and
                  Badge IDs between all internally-facing backend systems. The
                  service scaled to handle 1000 TPS across 12 APIs while
                  maintaining data integrity and confidentiality.

            \item Led and mentored team to deliver a Kotlin-based Android App
                  for Amazon One clients to seamlessly verify 21+ eligibility
                  of a customer using a palm hover. Worked with product to
                  devise a user workflow that fit device constraints between
                  the off-the-shelf Android device framework and the custom AO
                  device, collaborating with the AO device framework owners
                  where needed. Extended data integrity and confidentiality
                  from backend systems while maintaining a low-latency user
                  experience between devices.

            \item Collaborated across teams to add Starbucks Gift Card support
                  to the Amazon One palm hover experience for fast checkout.
                  Extended backend systems to map 3rd party identifiers, such
                  as a Gift Card barcode, to internal biometric identifiers
                  on-device through a secure API.

        \end{itemize}

        \vspace{-0.2cm}
        \centerline{\rule{0.3\linewidth}{0.4pt}}
        \vspace{-0.2cm}

        \item[Amazon - Whole Foods Market]
        \hfill
        \textit{Sept 2018 - May 2022}
        \vspace{-.1cm}
        \begin{itemize}[leftmargin=*]
            \item Drove \$40M in operational savings by developing and rolling
                  out an Inventory Restocking application running on enterprise
                  handheld scanners (Honeywell), enabling store associates to
                  scan and submit store items to vendors for store
                  replenishment. Launched an MVP in 10 pilot stores and scaled
                  to over 500 WFM stores nationwide.

            \item Architected and mentored team through extensions for the
                  Inventory Restocking application to have it proactively
                  suggest items to store associates. Negotiated new app
                  workflow and API contracts with product and UX to deliver
                  single and batch APIs to handle high event throughput to meet
                  customer needs. Prioritized delivery to meet MVP and
                  production rollout phases. Deployed background jobs that
                  would scale to the processing of millions of item events
                  daily at peak without impacting on-site store operations.

            \item Led design and implementation of smart dashcart checkout
                  to enable "Just Walk Out" shopping. Delivered a
                  workflow solution triggered by a customer entering a
                  'checkout zone' to auto-charge the customer and send email
                  receipts upon store exit. Used serverless architecture to
                  keep overhead at a minimum and enable monitoring via
                  observable metrics.
        \end{itemize}

        \vspace{-0.2cm}
        \centerline{\rule{0.3\linewidth}{0.4pt}}
        \vspace{-0.1cm}

        \item[Space and Naval Warfare Systems Command (SPAWAR) via SAIC]
        \hfill
        \vspace{-.1cm}
        \textit{May 2017 - July 2018}
        \begin{itemize}[leftmargin=*]
            \item Engineered mission-critical infrastructure automation for v22
                  Osprey support, securing data environments via dynamic Layer
                  3 proxy routing and application firewalls. Reduced deployment
                  friction while strictly adhering to defense-grade security
                  standards.
        \end{itemize}

        \end{description}

    \item[\textsf{\fontfamily{ptm}\selectfont TECHNICAL SKILLS}]
        \hfill
        \vspace{-.3cm}
        \rule{\linewidth}{1.0pt}
        \par
        \vspace{0.01cm}\noindent
        \begin{tabularx}{\linewidth}{>{\arraybackslash}r|X}
            \multirow{1}{*}{Languages}
                & Java, Kotlin, Python, Javascript
                  (\textit{TypeScript, NodeJs, AngularJs}), Bash \\

            \multirow{1}{*}[.5em]{\shortstack[r]{Infrastructure\\App Components}}
                & $\left( \begin{tabular}{@{}l|l|l@{}}
                    Compute; \textit{EC2, Fargate, Lambda} &
                    Object Storage; \textit{S3} &
                    Infra Code; \textit{CDK, Ansible} \\
                    Database; \textit{DynamoDB, PostgreSQL} &
                    Warehousing; \textit{Redshift, MongoDb} &
                    DNS \& Routing; \textit{Route 53} \\
                    Events; \textit{SNS, KAFKA, RabbitMQ} &
                    Workflows; \textit{SWF} &
                    Networking; \textit{VPC}
                  \end{tabular} \right)$ \\

            \multirow{1}{*}{\shortstack{Infra Monitoring}}
                & AWS Cloudwatch Service; Structured Logs, Log Groups, Metrics,
                 Alarms, Dashboards \\

            \multirow{1}{*}{\shortstack{Infra Support}}
                & Support Ticketing, Generation, Response, Runbooks\\

            \multirow{1}{*}{\shortstack{Dev Env}}
                & Linux,
                  Android,
                  GIT,
                  VMWare/VirtualBox,
                  Kubernetes/Docker,
                  AWS,
                  Regex \\
        \end{tabularx}

        \item[\textsf{\fontfamily{ptm}\selectfont EDUCATION}]
        \hfill
        \vspace{-.3cm}
        \rule{\linewidth}{1.0pt}
        \par
        \vspace{0.01cm}\noindent
            \begin{tabularx}{\linewidth}{>{\arraybackslash}l|X}
            \multirow{2}{*}{
                \shortstack{
                    \textbf{University of California, San Diego}
                }
            }
                & B.S. Joint Mathematics and Computer Science\\
                & B.S. Cognitive Science \textit{with specialization in Machine
                  Learning and AI} \\
            \end{tabularx}

\end{description}
\end{document}
